---
title: "P8158 Final"
author: "Waveley Qiu (wq2162)"
date: "2022-04-14"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
## Interested Variables

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE)
library(sem)
library(semPlot)
library(psych)
source("shared_code/data_prep_and_setup.R")
```

## Construct Reliability: Dedication to Sport/ athlete identity

```{r}
athletic_identity <- c("cnsdr_ath", "sprt_goals", "frnds_ath", "sprt_impt", "think_sprt", "bad_sprt", "dprs_sprt")
```
Chronbach's alpha is 0.74, with a 95 \% confidence interval of (0.70, 0.78).

Chronbach's alpha is 0.91, with a 95 \% confidence interval of (0.90, 0.91).

## Latent Variables

LV1:dedication_to_sport
CNSDR_ATH: I consider myself an athlete
SPRT_GOALS: I have many goals related to sport
FRNDS_ATH: Most of my friends are athlete
SPRT_IMPT: Sport is the most important part of my life
THINK_SPRT: I spend more time thinking about sport than anything else
SPRT_LVL: Sport level

LV2:positive_outlook
HAPPY: Happy
INT_LIFE: Interested in life
SATISFIED: Satisfied
CONT_SOC: That you had something important to contribute to society

LV3:interaction_society
BELONG: That you belonged to a community (like a social group or neighbourhood)
BET_SOC: That our society is becoming a better place for people like you
PEOPLE_GOOD: That people are basically good
SENSE_SOC: That the way our society works makes sense to you

LV4: maturity
LIKE_PER: That you liked most parts of your personality
RESPONSIBLE: Good at managing the responsibilities of your daily life
WARM_REL: That you had warm and trusting relationships with others
CHAL_EXP: That you had experiences that challenged you to grow and become a better person
EXP_IDEA: Confident to think or express your own ideas and opinions
MEANING: That your life has a sense of direction or meaning to it

LV5: resilience
BOUNCE: I ten-d to bounce back quickly after hard times
STRS_EVNT: I have a hard time making it through stressful events
STRS_RCVR: It does not take me long to recover from a stressful event
SNAP_BACK: It is hard for me to snap back when something bad happens
DIFFICULT: I usually come through difficult times with little trouble
SETBACKS: I tend to take a long time to get over setbacks in my life

```{r}
 athlete_sem2 <- '
  # measurement model
    external_identity =~ sprt_goals + cnsdr_ath + frnds_ath
    internal_value =~ sprt_impt + think_sprt
    negative_events =~ dprs_sprt + bad_sprt
    
    athlete_identity =~ external_identity + internal_value + negative_events
    
    healthy_lifestyle =~ hr_sleep + smoking + fruit_veg
    
    resilience =~ bounce + strs_evnt + strs_rcvr + snap_back + difficult + setbacks
    
  # structural model - direct effects
    mhc_sf ~ a*athlete_identity + b*healthy_lifestyle + c*resilience
    resilience ~ d*athlete_identity
    healthy_lifestyle ~ e*athlete_identity

  # indirect
    indirect_athlete_identity := d*c + e*b

  # total
    total_athlete_identity:= d*c + a + e*b
'

athlete_sem_fit2 <- sem(athlete_sem2, 
                       data = athletes, 
                       sample.cov = TRUE, 
                       missing = "ML")
summary(athlete_sem_fit2)

semPaths(athlete_sem_fit2,
         what = "paths",
         whatLabels = "std", 
         reorder = FALSE,
         layout = "tree2",
         rotation = 2,
         intercepts = FALSE)
```

## Boxplot of MHC_SF between athlete and non-athlete
```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_classic() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "brewer",
  ggplot2.continuous.fill = "brewer"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

# MHC_SF
MHC_SF <- c("mhc_sf", "athlete_yn")

MHC_SF_numeric <- dataset[,MHC_SF] %>% mutate(
  mhc_sf= as.numeric(mhc_sf),
  athlete_yn = as.factor( athlete_yn)) %>% mutate(
  athlete_yn = case_when(
    athlete_yn == "1" ~ "Athlete",
    athlete_yn == "2" ~ "Non-athlete"
  )
)

# Resilience
resilience <- c( "athlete_yn","bounce", "strs_evnt", "strs_rcvr", "snap_back", "difficult", "setbacks")

resilience_numeric <- dataset[,resilience] %>% map_df(., as.numeric) %>% mutate(
  athlete_yn = case_when(
    athlete_yn == "1" ~ "Athlete",
    athlete_yn == "2" ~ "Non-athlete"
  )
)

resilience_matrix <- resilience_numeric %>% as.matrix()

ath_resilience_numeric = resilience_numeric %>% mutate(
  total_resilience_score = bounce + strs_evnt + strs_rcvr + snap_back + difficult + setbacks,
  athlete_yn= as.factor(athlete_yn)
)


athe_res = cbind(MHC_SF_numeric, ath_resilience_numeric[,8])
colnames(athe_res) = c("Sum_Score_MHC",'athlete_yn','Total_Resilience_Score')
gtsummary::tbl_summary(athe_res, by = athlete_yn) %>% add_p() %>% add_n()
```

# correlation

```{r}

external = dataset[,18:19] %>% map_df(., as.numeric) %>% mutate(external_score = (cnsdr_ath + sprt_goals)/2)

internal = dataset[,21:22] %>% map_df(., as.numeric) %>% mutate(internal_score = (sprt_impt + think_sprt)/2)

negative = dataset[,23:24]%>% map_df(., as.numeric) %>% mutate(negative_score = (dprs_sprt + bad_sprt)/2)

cor_data = cbind(athe_res,external,internal, negative) %>%
  mutate(
  total_AIMS = (external_score + internal_score + negative_score)/3
)

cor_data_2 = cor_data %>% select(Sum_Score_MHC, athlete_yn, Total_Resilience_Score,external_score, internal_score, negative_score,total_AIMS) 

library(corrplot)
round(cor(cor_data_2[-2] %>% na.omit()),digits = 2) %>% knitr::kable()
tbl_summary(cor_data_2, by = athlete_yn) %>% add_p()
```


