---
title: "waveley_attempt"
author: "Waveley Qiu (wq2162)"
date: "2022-04-30"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE)
library(sem)
library(semPlot)
source("shared_code/data_prep_and_setup.R")
```

How does an athlete's measure of athletic identity affect MHC-SF, as mediated through resilience and a healthy lifestyle?

# Latent Variable Construction

## Latent Variable 1: Athletic Identity

First, let's select the variables we are interested in.

```{r}
athletic_identity <- c("cnsdr_ath", "sprt_goals", "frnds_ath", "sprt_impt", "think_sprt", "bad_sprt", "dprs_sprt")

athletic_identity_numeric <- athletes[,athletic_identity] %>% map_df(., as.numeric)

athletic_identity_matrix <- athletic_identity_numeric %>% as.matrix()
```

### Polychoric Correlations

Now, let us determine the number of factors that might underlie these variables.

```{r}
athlete_parallel <- fa.parallel(athletic_identity_matrix, cor = "poly", fa = "pc")
athlete_parallel$pc.values
```

PCA indicates that two factors underlie these variables.

### EFA

We now want to examine which variables might load on which factors. To do so, we will perform EFA on a 2-factor model, and also on 1- and 3- factor models.

First, the 2-factor model:

```{r}
athletic_efa2 <- fa(r = athletic_identity_matrix, nfactors = 2, cor = "poly")
fa.diagram(athletic_efa2, digits = 2, simple = TRUE)
```

Now, the 3-factor model:

```{r}
athletic_efa3 <- fa(r = athletic_identity_matrix, nfactors = 3, cor = "poly")
fa.diagram(athletic_efa3, digits = 2, simple = TRUE)
```

Now, the 1-factor model:

```{r}
athletic_efa1 <- fa(r = athletic_identity_matrix, nfactors = 1, cor = "poly")
fa.diagram(athletic_efa1, digits = 2, simple = TRUE)
```

The 3-factor model seems to fit the data the best, as it has the smallest BIC. We will proceed by using the 3-factor model for athletic_identity.

### Reliability

LV 1: External Identity

```{r}
external_identity <- c("cnsdr_ath", "sprt_goals", "frnds_ath")

external_identity_numeric <- athletes[,external_identity] %>% map_df(., as.numeric)

external_identity_matrix <- external_identity_numeric %>% as.matrix()
psych::alpha(external_identity_matrix)
```

LV 2: Internal Value

```{r}
internal_value <- c("sprt_impt", "think_sprt")

internal_value_numeric <- athletes[,internal_value] %>% map_df(., as.numeric)

internal_value_matrix <- internal_value_numeric %>% as.matrix()
psych::alpha(internal_value_matrix)
```

LV 3: Negative Events

```{r}
negative_events <- c("dprs_sprt", "bad_sprt")

negative_events_numeric <- athletes[,negative_events] %>% map_df(., as.numeric)

negative_events_matrix <- negative_events_numeric %>% as.matrix()
psych::alpha(negative_events_matrix)
```

Our final model for athlete_identity is as follows:

external_identity = sprt_goals + cnsdr_ath + frnds_ath
internal_value = sprt_impt + think_sprt
negative_events = dprs_sprt + bad_sprt

### CFA

```{r}
athlete_model <- 
'external_identity =~ sprt_goals + cnsdr_ath + frnds_ath
 internal_value =~ sprt_impt + think_sprt
 negative_events =~ dprs_sprt + bad_sprt'

athlete_CFA = cfa(athlete_model, data = athletic_identity_matrix,
                   ordered = names(athletic_identity_matrix),
                   std.lv = TRUE)
summary(athlete_CFA, fit.measures = TRUE)
```

## Latent Variable 2: Healthy Lifestyle

```{r}
healthy_lifestyle <- c("hr_sleep", "smoking", "fruit_veg")

healthy_life_numeric <- athletes[,healthy_lifestyle] %>% map_df(., as.numeric)

healthy_life_matrix <- healthy_life_numeric %>% as.matrix()
```

### Polychoric Correlations

Now, let us determine the number of factors that might underlie these variables.

```{r}
health_parallel <- fa.parallel(healthy_life_matrix, fa = "pc")
health_parallel$pc.values
```

1 latent factor appears to underlie these variables. *** need to check if this is the correct way to assess formative LV's ***

## Latent Variable 3: Resilience

Finally, we will look at resilience. 

```{r}
resilience <- c("bounce", "strs_evnt", "strs_rcvr", "snap_back", "difficult", "setbacks")

resilience_numeric <- athletes[,resilience] %>% map_df(., as.numeric)

resilience_matrix <- resilience_numeric %>% as.matrix()
```

### Polychoric Correlations

```{r}
resilience_parallel <- fa.parallel(resilience_matrix, fa = "pc")
resilience_parallel$pc.values
```

It appears that a 1-factor model will sufficiently explain the variability across these variables.

### EFA

First, we can do a 1-factor EFA model:

```{r}
resilience_efa1 <- fa(r = resilience_matrix, nfactors = 1, cor = "poly")
fa.diagram(resilience_efa1, digits = 2, simple = TRUE)
summary(resilience_efa1)
```

Now, we can try a 2-factor EFA model:

```{r}
resilience_efa2 <- fa(r = resilience_matrix, nfactors = 2, cor = "poly")
fa.diagram(resilience_efa2, digits = 2, simple = TRUE)
resilience_efa2
```

Finally, we can try a 3-factor EFA model:

```{r}
resilience_efa3 <- fa(r = resilience_matrix, nfactors = 3, cor = "poly")
fa.diagram(resilience_efa3, digits = 2, simple = TRUE)
summary(resilience_efa3)
```


### Reliability

```{r}
psych::alpha(resilience_matrix)
```

Chronbach's alpha is 0.89 (0.88, 0.91). No items can be dropped to improve this measure, so we will keep all of them in this latent variable.


# Final CFA

```{r}
final_model <- 
'external_identity =~ sprt_goals + cnsdr_ath + frnds_ath
 internal_value =~ sprt_impt + think_sprt
 negative_events =~ dprs_sprt + bad_sprt
 
 athlete_identity =~ external_identity + internal_value + negative_events
 
 healthy_lifestyle =~ hr_sleep + smoking + fruit_veg
 
 resilience =~ bounce + strs_evnt + strs_rcvr + snap_back + difficult + setbacks
'
fin_df <- athletes %>% map_df(., as.numeric)

final_cfa = cfa(final_model, 
                data = fin_df,
                std.lv = TRUE)
summary(final_cfa, fit.measures = TRUE)
```

## Modification Indices

```{r}
modindices(final_cfa, power = TRUE, sort = TRUE, minimum.value = 10) 
```

# Structural Equation Modeling

```{r}

athlete_sem <- '
  # measurement model
    external_identity =~ sprt_goals + cnsdr_ath + frnds_ath
    internal_value =~ sprt_impt + think_sprt
    negative_events =~ dprs_sprt + bad_sprt
    
    athlete_identity =~ external_identity + internal_value + negative_events
    
    healthy_lifestyle =~ hr_sleep + smoking + fruit_veg
    
    resilience =~ bounce + strs_evnt + strs_rcvr + snap_back + difficult + setbacks
    
  # structural model - direct effects
    mhc_sf ~ a*athlete_identity + b*healthy_lifestyle + c*resilience
    resilience ~ d*athlete_identity
    healthy_lifestyle ~ e*athlete_identity

  # indirect
    indirect_athlete_identity := d*c

  # total
    total_athlete_identity:= d*c + a
'

athlete_sem_fit <- sem(athlete_sem, 
                       data = athletes, 
                       sample.cov = TRUE, 
                       missing = "ML")
summary(athlete_sem_fit)
semPaths(athlete_sem_fit,
         whatLabels = "std", 
         reorder = FALSE,
         layout = "tree2")

# graph looks cleaner
semPaths(athlete_sem_fit,
         what = "paths",
         whatLabels = "std", 
         reorder = FALSE,
         layout = "tree2",
         rotation = 3,
         intercepts = FALSE)
```

Double headed arrow between healthy lifestyle and athlete identity means that they may share a common cause and their direct causal relationship is unspecified. We hypothesize that athlete identity causes healthy lifestyle. We can change the double headed arrow to direct causal arrow.


```{r}


athlete_sem <- '
  # measurement model
    external_identity =~ sprt_goals + cnsdr_ath + frnds_ath
    internal_value =~ sprt_impt + think_sprt
    negative_events =~ dprs_sprt + bad_sprt
    
    athlete_identity =~ external_identity + internal_value + negative_events
    
    resilience =~ bounce + strs_evnt + strs_rcvr + snap_back + difficult + setbacks
    
  # structural model - direct effects
    mhc_sf ~ a*athlete_identity + c*resilience
    resilience ~ d*athlete_identity

  # indirect
    indirect_athlete_identity := d*c

  # total
    total_athlete_identity:= d*c + a
'

athlete_sem_fit <- sem(athlete_sem, 
                       data = athletes, 
                       sample.cov = TRUE, 
                       missing = "ML")
summary(athlete_sem_fit)
semPaths(athlete_sem_fit,
         whatLabels = "std", 
         reorder = FALSE,
         layout = "tree2")

# graph looks cleaner
semPaths(athlete_sem_fit,
         what = "paths",
         whatLabels = "std", 
         reorder = FALSE,
         layout = "tree2",
         rotation = 1,
         intercepts = FALSE)
```

## Interpretation

From our SEM, we observe that athlete identity *negatively* affects emotional well being, as defined by the MHC-SF scale. Resilience is associated with a positive effect on MHC-SF. Healthy lifestyle habits are also associated with a positive effect on MHC-SF. 

Athletic identity is positively associated with resilience. 


























